---
title: "Quantium Virtual Internship - Retail Strategy and Analytics - Task 1"
author: "Abu RIjal"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Install and load necessary packages:

  * `tidyverse`
  * `readxl`

```{r load library, results='hide'}

library(tidyverse)
library(readxl) 

```

## Import data 

```{r Dataset,results='hide'}

transactionData = read_excel("QVI_transaction_data.xlsx")
customerData = read_csv("QVI_purchase_behaviour.csv")

```

## Exploratory data analysis

### Examining transaction data

```{r str}

str(transactionData)

```

```{r head}

transactionData

```

#### Convert DATE column to a date format

```{r Convert DATE to date format}

transactionData$DATE = as.Date(transactionData$DATE, origin = "1899-12-30")

```

#### Check

```{r check}

transactionData

```

We should check that we are looking at the right products by examining PROD_NAME.

```{r}

transactionData %>% 
  count(PROD_NAME)

```
Looks like we are definitely looking at potato chips but how can we check that
these are all chips? We can do some basic text analysis by summarising the
individual words in the product name.

```{r}

trans1 = transactionData %>% 
  separate(PROD_NAME,into=c("Brand name","type"),sep=" ")

head(trans1)

```



